### 2019-09-30 conflog.tex
adds quotes, and general updates

We propose the conference be held on either of the following dates: 
\begin{enumerate}
	\item Thursday, April 8$^{th}$ - Sunday, April 11$^{th}$ 
	\item Thursday, April 15$^{th}$ - Sunday, April 18$^{th}$
\end{enumerate}
We believe either of these dates would serve as an appropriate first choice because they avoid major conflict dates like finals and spring break for most schools. Additionally, mid-April offers pleasant, mild, weather in Champaign. The reason for proposing two weekends to host the conference is due to the UIUC tradition of hosting Mom's Weekend on or near the first weekend in April. The Illinois Mom's Association has not yet announced their 2021 dates but, to avoid potential conflict, we suggest two dates. In the event that both of these dates are unavailable our backup date is 
\begin{itemize}
	\item Thursday, April 1$^{st}$ - Sunday, April 4$^{th}$.  
\end{itemize}
This is a backup date because Easter falls on that Sunday. In general, this should be avoided. In this case we found that holding the conference at the end of April would conflict with finals for students and holding it earlier in March would conflict with several spring breaks as well as having potentially poorer weather. A detailed conflict schedule is listed in Appendix A.

@@

The Illini Union is capable of hosting the entire technical program of the ANS Student Conference. This keeps the conference contained in one convenient location while being within easy access of the rest of the campus. Technical sessions will be held in a combination of rooms on the second, third, and fourth floors of The Union. Each of these rooms have at least enough capacity for 42 people, lecture style, and A/V capability. There will also be rooms available to have panels and workshops during the course of the technical program. The Illini Rooms A and B will be a combined space for the career fair while Illini Room C and the south lounge will host the poster sessions. We will keep the space open to allow the poster sessions and career fair to share attendance and encourage networking. A detailed list of room capacities and floor plans are located in Appendix D: Building Layout. \\

@@

\subsection{Conference Contingency Plan}
In the event that the Union has reduced availability during the conference we have the ability to host technical sessions and workshops at a combination of buildings: The National Center for Supercomputing Applications (NCSA) and Beckman Institute. Rooms in Beckman Institute range from 20 - 60 classroom capacity. Most rooms have A/V capabilities. NCSA has rooms that can hold 13 - 50 people in lecture style. As these buildings are UIUC property, the cost of renting them are significantly reduced compared to a private facility. Additionally, these two buildings are adjacent to one another and are at most a 10 minute walk from the Union. We could also host all technical sessions at the I Hotel. Hosting at the I Hotel is more expensive than hosting in University buildings and would also require additional transportation options. We would need to reevaluate some parts of our budget in order to host the technical program at this venue. See Appendix E for a map marking the locations of the proposed conference facilities.\\

@@

$\textbf{The Garden Hotel Urbana}$\\
When selecting the primary hotel to accommodate students we considered the ability to host all students under one roof over proximity to the conference activities. The Garden Hotel Urbana (soon to be the Radisson) will be the primary hotel for all attendees. Since this hotel is just beyond walking distance from the main conference activities, regular transportation to and from the Union will be provided during peak commuting hours (8am-10am $\&$ 3pm-5pm). Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 8am to 6pm. This will also be the location of the opening ceremony dinner.\\ 
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_king.jpg}
		\subcaption{King Suite}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_queen.jpg}
		\subcaption{Queen Double}
	\end{subfigure}
	\caption{Garden Urbana Hotel rooms}		
\end{figure}

@@

{\centering
\begin{tabular}{lccccc}
\hline\hline
\textbf{Hotel} & \textbf{Distance from the Union (mi)} & \textbf{Dates} & \textbf{Number of Rooms} & \textbf{Rates*} & \textbf{Per Person**}\\
\hline\hline
Garden Urbana & 2.2  & 4/8-4/11 & 198 & 119 & $\$$29.75\\
Illini Union & 0.0 & 4/8-4/11 & 35 & 134 & $\$$33.5\\
Marriott TowneSuites &0.25 & 4/8-4/11 & 95 & 189 & \$47.50\\ 
\hline
\end{tabular}}
\textbf{*}\textit{Price for a queen double}
\textbf{**}\textit{Assumes 4 people per room}

\subsection{Dining}
\subsubsection{Breakfast}
Our primary hotel, the Garden Hotel in Urbana, soon to be the Radisson Hotel, serves complimentary breakfast every morning. Due to this, we will not be catering breakfast at the Illini Union during the conference. Guests staying at the Illini Union Hotel are provided with vouchers for breakfast at the food court in the basement of the Union. The food court offers Einstein Brothers, Starbucks, Garbanzo Mediterranean, and more. 
\subsubsection{Lunch}
\subsubsection{Dinner}

@@

\subsubsection{Getting to the Conference}
The primary hotel, Garden Hotel Urbana, is approximately two miles from the Union and outside of reasonable walking distance. Thus we have budgeted to include transportation provided by Peoria Charter. We intend to have busses shuttling continuously between the Union and the Garden Hotel Urbana. For those who desire more flexibility and freedom, there is CU-MTD bus stop adjacent to the hotel that has a bus every 10 minutes. This bus route, the 22 Illini, can take attendees directly to the Union from the hotel. It is also one of the main campus bus routes and can take travelers almost anywhere on or around campus. Lyft and Uber are available as well for attendees that choose to use those services. A map of the bus route is in Appendix E: Campus Map of Locations.

\begin{table}[H]
\caption{Airfare to Chicago/Champaign}
\label{table:airfare}
   \begin{tabular}{lccc}
   	\hline\hline
    \textbf{School} & \textbf{Departure City} & \textbf{O'Hare (ORD)*} & \textbf{Willard (CMI)} \\
    \hline\hline
    University of California - Berkeley & San Francisco (SFO) & $\$$338 & $\$$436 \\
    University of California - Irvine&Orange County (SNA)&$\$$394&$\$$436\\
    Colorado School of Mines & Denver (DEN) & $\$$222 & $\$$328 \\
    Three Rivers Community College & Hartford (BDL) & $\$$468 & $\$$327 \\ 
    University of Florida & Gainesville (GNV)& $\$$377 & $\$$416 \\
    Georgia Institute of Technology & Atlanta (ATL)& $\$$199 & $\$$291 \\
    Southern Polytechnic State University & Atlanta (ATL) & $\$$199 & $\$$291 \\
    Idaho State University & Idaho Falls (IDA) & $\$$501 & NA \\
    Kansas State University & Manhattan (MHK) & $\$$336 & $\$$406 \\ 
    Louisiana State University & Baton Roughe (BTR) & $\$$380 & $\$$329 \\
    United States Naval Academy & Hanover (BWI) & $\$$210 & $\$$321 \\  
    University of Maryland & Hanover (BWI)&$\$$210 &$\$$321 \\ 
    Massachusetts Institute of Technology & Boston (BOS)&$\$$191 &$\$$325 \\ 
    University of Massachusetts - Lowell &Boston (BOS) &$\$$191 &$\$$325 \\
    University of Nevada - Las Vegas & Las Vegas (LAS)& $\$$262 &$\$$358 \\ 
    University of New Mexico &Albuquerque (ABQ) &$\$$439 &$\$$358 \\ 
    City College of New York &$\$$New York (JFK) &$\$$245 &$\$$325 \\
    Excelsior College & Albany (ALB) &$\$$444 &$\$$327 \\ 
    Rensselaer Polytechnic Institute & Albany (ALB)&$\$$444 &$\$$327 \\ 
    United States Military Academy at West Point&New Windsor (SWF)&$\$$273 &$\$$357 \\ 
    North Carolina State University &Morrisville (RDU) &$\$$180 &$\$$321 \\
    Oregon State University &Portland (PDX) &$\$$314 &$\$$436 \\ 
    Pennsylvania State University & Harrisburg (MDT)&$\$$397 & $\$$323 \\
    University of Pittsburgh &Pittsburgh (PIT) &$\$$282 &$\$$293 \\ 
    Clemson University&Greenville (GSP)&$\$$356&$\$$287\\
    South Carolina State University&Columbia (CAE)&$\$$407 &$\$$564 \\ 
    University of South Carolina&Columbia (CAE)&$\$$407&$\$$564\\
    Chattanooga State Comunity College&Chattanooga (CHA)&$\$$334&$\$$316\\
    University of Tennessee&Knoxville (TYS)&$\$$340&$\$$291\\
    Texas A\&M University&College Station (CLL)&$\$$367&$\$$243\\
    University of Texas - Arlington&Dallas (DFW)&$\$$197&$\$$303\\
    University of Texas - Austin&Austin (AUS)&$\$$298&$\$$358\\
    University of Texas - Permian Basin&Midland (MAF)&$\$$434&$\$$333\\
    Utah State University&Salt Lake City (SLC)&$\$$298&$\$$358\\
    University of Utah&Salt Lake City (SLC)&$\$$298&$\$$358\\
    Virginia Commonwealth University&Richmond (RIC)&$\$$279&$\$$321\\
    University of Washington&Seattle (SEA)&$\$$253&$\$$436\\
    \hline
    Average Lowest Cost for Air Travel**&$\$$293&&
    \end{tabular} 
\end{table}

>>>>

We propose the conference be held on either of the following dates: 
\begin{enumerate}
	\item Thursday, April 8$^{th}$ - Sunday, April 11$^{th}$ 
	\item Thursday, April 15$^{th}$ - Sunday, April 18$^{th}$
\end{enumerate}
We believe either of these dates would serve as an appropriate first choice because they avoid major conflict dates like finals and spring break for most schools. Additionally, mid-April offers pleasant, mild, weather in Champaign. The reason for proposing two weekends to host the conference is due to the UIUC tradition of hosting Mom's Weekend on or near the first weekend in April. The Illinois Mom's Association has not yet announced their 2021 dates but, to avoid potential conflict, we suggest two dates. In the event that both of these dates are unavailable our backup date is 
\begin{itemize}
	\item Thursday, April 1$^{st}$ - Sunday, April 4$^{th}$.  
\end{itemize}
This is a backup date because Easter falls on that Sunday. In general, this should be avoided. In this case we found that holding the conference at the end of April would conflict with finals for students and holding it earlier in March would conflict with several spring breaks as well as having potentially poorer weather. A detailed conflict schedule is listed in Appendix A on page \pageref{appendix:schedule}.

@@

The Illini Union is capable of hosting the entire technical program of the ANS Student Conference. This keeps the conference contained in one convenient location while being within easy access of the rest of the campus. Technical sessions will be held in a combination of rooms on the second, third, and fourth floors of The Union. Each of these rooms have at least enough capacity for 42 people, lecture style, and A/V capability. There will also be rooms available to have panels and workshops during the course of the technical program. The Illini Rooms A and B will be a combined space for the career fair while Illini Room C and the south lounge will host the poster sessions. We will keep the space open to allow the poster sessions and career fair to share attendance and encourage networking. A detailed list of room capacities and floor plans are located in Appendix D: Building Layout on page \pageref{appendix:building}. \\

@@

\subsection{Conference Contingency Plan}
In the event that the Union has reduced availability during the conference we have the ability to host technical sessions and workshops at a combination of buildings: The National Center for Supercomputing Applications (NCSA) and Beckman Institute. Rooms in Beckman Institute range from 20 - 60 classroom capacity. Most rooms have A/V capabilities. NCSA has rooms that can hold 13 - 50 people in lecture style. As these buildings are UIUC property, the cost of renting them are significantly reduced compared to a private facility. Additionally, these two buildings are adjacent to one another and are at most a 10 minute walk from the Union. We could also host all technical sessions at the I Hotel. Hosting at the I Hotel is more expensive than hosting in University buildings and would also require additional transportation options. We would need to reevaluate some parts of our budget in order to host the technical program at this venue. See Appendix E on page \pageref{appendix:map} for a map marking the locations of the proposed conference facilities.\\

@@

$\textbf{The Garden Hotel Urbana}$\\
When selecting the primary hotel to accommodate students we considered the ability to host all students under one roof over proximity to the conference activities. The Garden Hotel Urbana (soon to be the Radisson) will be the primary hotel for all attendees. This will also be the location of the opening ceremony dinner. Since this hotel is just beyond walking distance from the main conference activities, we will hire four Peoria Charter busses to shuttle attendees to and from the Union every 10 minutes. Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 8am to 6pm. \\ 
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_king.jpg}
		\subcaption{King Suite}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_queen.jpg}
		\subcaption{Queen Double}
	\end{subfigure}
	\caption{Garden Urbana Hotel rooms}		
\end{figure}

@@

\begin{table}
\caption{Cost of Hotels}
\label{table:hotels}
	\centering
	\makebox[0.6\linewidth]{\begin{tabular}{lccccc}
	\hline\hline
	\textbf{Hotel} & \textbf{Distance from the Union (mi)} & \textbf{Dates} & \textbf{Number of Rooms} & \textbf{Rates*} & \textbf{Per Person**}\\
	\hline\hline
	Garden Urbana & 2.2  & 4/8-4/11 & 198 & 119 & $\$$29.75\\
	Illini Union & 0.0 & 4/8-4/11 & 35 & 134 & $\$$33.5\\
	Marriott TowneSuites &0.25 & 4/8-4/11 & 95 & 189 & \$47.50\\ 
	\hline
	\end{tabular}}
\end{table}
\textbf{*}\textit{Price for a queen double}
\textbf{**}\textit{Assumes 4 people per room}

\subsection{Dining}
\subsubsection{Breakfast}
Our primary hotel, the Garden Hotel in Urbana, soon to be the Radisson Hotel, serves complimentary breakfast every morning. Due to this, we will not be catering breakfast at the Illini Union during the conference. Guests staying at the Illini Union Hotel are provided with vouchers for breakfast at the food court in the basement of the Union. The food court offers Einstein Brothers, Starbucks, Garbanzo Mediterranean, and more. 
\subsubsection{Lunch}
Conference attendees are encouraged to explore the University’s campus and surroundings, including getting lunch on the main street of campus, Green street. Due to this, lunch will not be provided for the conference. However, box lunches will be provided for the Student Sections Committee meeting from 11:30pm to 1:30pm on Friday as well as any lunch and learns hosted by sponsors on Friday and Saturday. The Illini Union’s catering service, University Catering, will be used. Sponsors can also choose to sponsor and host a lunch in one of the technical session rooms on Friday or Saturday. If more rooms are required, there are available rooms on the first and second floor of the Union. Sponsors will be able to use University Catering, or cater from one of the food vendors in the Illini Union.
\subsubsection{Dinner}

@@

\subsubsection{Getting to the Conference}
The primary hotel, Garden Hotel Urbana, is approximately two miles from the Union and outside of reasonable walking distance. Thus we have budgeted to include transportation provided by Peoria Charter. We intend to have busses shuttling continuously between the Union and the Garden Hotel Urbana. For those who desire more flexibility and freedom, there is CU-MTD bus stop adjacent to the hotel that has a bus every 10 minutes. This bus route, the 22 Illini, can take attendees directly to the Union from the hotel. It is also one of the main campus bus routes and can take travelers almost anywhere on or around campus. Lyft and Uber are available as well for attendees that choose to use those services. A map of the bus route is in Appendix E: Campus Map of Locations on page \pageref{appendix:map}.

\begin{table}[H]
\caption{Airfare to Chicago/Champaign}
\label{table:airfare}
   \begin{tabular}{lccc}
   	\hline\hline
    \textbf{School} & \textbf{Departure City} & \textbf{O'Hare (ORD)*} & \textbf{Willard (CMI)} \\
    \hline\hline
    University of California - Berkeley & San Francisco (SFO) & $\$$338 & $\$$436 \\
    University of California - Irvine&Orange County (SNA)&$\$$394&$\$$436\\
    Colorado School of Mines & Denver (DEN) & $\$$222 & $\$$328 \\
    Three Rivers Community College & Hartford (BDL) & $\$$468 & $\$$327 \\ 
    University of Florida & Gainesville (GNV)& $\$$377 & $\$$416 \\
    Georgia Institute of Technology & Atlanta (ATL)& $\$$199 & $\$$291 \\
    Southern Polytechnic State University & Atlanta (ATL) & $\$$199 & $\$$291 \\
    Idaho State University & Idaho Falls (IDA) & $\$$501 & NA \\
    Kansas State University & Manhattan (MHK) & $\$$336 & $\$$406 \\ 
    Louisiana State University & Baton Rouge (BTR) & $\$$380 & $\$$329 \\
    United States Naval Academy & Hanover (BWI) & $\$$210 & $\$$321 \\  
    University of Maryland & Hanover (BWI)&$\$$210 &$\$$321 \\ 
    Massachusetts Institute of Technology & Boston (BOS)&$\$$191 &$\$$325 \\ 
    University of Massachusetts - Lowell &Boston (BOS) &$\$$191 &$\$$325 \\
    University of Nevada - Las Vegas & Las Vegas (LAS)& $\$$262 &$\$$358 \\ 
    University of New Mexico &Albuquerque (ABQ) &$\$$439 &$\$$358 \\ 
    City College of New York &\$New York (JFK) &$\$$245 &$\$$325 \\
    Excelsior College & Albany (ALB) &$\$$444 &$\$$327 \\ 
    Rensselaer Polytechnic Institute & Albany (ALB)&$\$$444 &$\$$327 \\ 
    United States Military Academy at West Point&New Windsor (SWF)&$\$$273 &$\$$357 \\ 
    North Carolina State University &Morrisville (RDU) &$\$$180 &$\$$321 \\
    Oregon State University &Portland (PDX) &$\$$314 &$\$$436 \\ 
    Pennsylvania State University & Harrisburg (MDT)&$\$$397 & $\$$323 \\
    University of Pittsburgh &Pittsburgh (PIT) &$\$$282 &$\$$293 \\ 
    Clemson University&Greenville (GSP)&$\$$356&$\$$287\\
    South Carolina State University&Columbia (CAE)&$\$$407 &$\$$564 \\ 
    University of South Carolina&Columbia (CAE)&$\$$407&$\$$564\\
    Chattanooga State Comunity College&Chattanooga (CHA)&$\$$334&$\$$316\\
    University of Tennessee&Knoxville (TYS)&$\$$340&$\$$291\\
    Texas A\&M University&College Station (CLL)&$\$$367&$\$$243\\
    University of Texas - Arlington&Dallas (DFW)&$\$$197&$\$$303\\
    University of Texas - Austin&Austin (AUS)&$\$$298&$\$$358\\
    University of Texas - Permian Basin&Midland (MAF)&$\$$434&$\$$333\\
    Utah State University&Salt Lake City (SLC)&$\$$298&$\$$358\\
    University of Utah&Salt Lake City (SLC)&$\$$298&$\$$358\\
    Virginia Commonwealth University&Richmond (RIC)&$\$$279&$\$$321\\
    University of Washington&Seattle (SEA)&$\$$253&$\$$436\\
    \hline
    Average Lowest Cost for Air Travel**&$\$$293&&
    \end{tabular} 
\end{table}

### 2019-09-30 proglog.tex
adds quotes, and general updates

\noindent{
\begin{minipage}{0.5\textwidth}
	\textbf{National Pentascale Computing Facility (NPCF)}\\
Also located on campus is NCSA, which houses Blue Waters, one of the most powerful supercomputers in the world. The NCSA is within walking distance from all conference hotels. During the tour, attendees will tour the machine room and witness some of the beautiful results it produces. Supercomputers like Blue Waters are important for solving computationally challenging problems and creating robust simulations for a variety of phenomena.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\includegraphics[width=\textwidth]{bw_front.png}
	\captionof{figure}{Blue Waters Supercomputer}
\end{minipage}
}

>>>>

\noindent{
\begin{minipage}{0.5\textwidth}
	\textbf{National Petascale Computing Facility (NPCF)}\\
Also located on campus is NCSA, which houses Blue Waters, one of the most powerful supercomputers in the world. The NCSA is within walking distance from all conference hotels. During the tour, attendees will tour the machine room and witness some of the beautiful results it produces. Supercomputers like Blue Waters are important for solving computationally challenging problems and creating robust simulations for a variety of phenomena.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\includegraphics[width=\textwidth]{bw_front.png}
	\captionof{figure}{Blue Waters Supercomputer}
\end{minipage}
}

### 2019-09-30 uiuc.tex
adds quotes, and general updates

The state of Illinois relies heavily on nuclear power to supply its energy needs with 52$\%$ of electricity generated by nuclear plants. The first human controlled nuclear reaction, Chicago Pile One, happened in Illinois. UIUC also bears a long tradition of nuclear power research and was home to the TRIGA nuclear reactor for almost 40 years. During this time researchers at UIUC made contributed to the knowledge store of nuclear reactor kinetics, isotope production, fission fragment physics, and much more. Now, UIUC is exploring ways to use nuclear power to accelerate its decarbonization efforts. This exploratory effort has the potential to position UIUC as the world leader in advanced carbon-free technologies. We hope to continue our excellent nuclear tradition by hosting the ANS Student Conference in 2021. 
\clearpage

\subsubsection{Accessibility and Accomodation}
Myriad festivals and sporting events on campus draw many people to Champaign-Urbana at various of the year, which means hotels are not hard to find. A large number of these hotels are located around downtown Champaign and the Eastern side of campus, making transportation easy. Champaign-Urbana Mass Transit (CU-MTD) is a reliable public transportation service that sees millions of riders every year. CU-MTD charges an affordable rate of \$1 per ride. All CU-MTD busses are wheelchair accessible. Rental bikes and rideshare services are also plentiful. There is a small airport, Willard Airport, just 20 minutes from campus that has regular flights to and from Chicago O’Hare and Dallas Fort Worth airports. Finally, Peoria Charter is a popular bus service with several daily trips between the UIUC campus and the Chicagoland area.

>>>>

The state of Illinois relies heavily on nuclear power to supply its energy needs with 52$\%$ of electricity generated by nuclear plants. The first human controlled nuclear reaction, Chicago Pile One, happened in Illinois. UIUC also bears a long tradition of nuclear power research and was home to the TRIGA nuclear reactor for almost 40 years. During this time researchers at UIUC contributed to the knowledge store of nuclear reactor kinetics, isotope production, fission fragment physics, and much more. Now, UIUC is exploring ways to use nuclear power to accelerate its decarbonization efforts. This exploratory effort has the potential to position UIUC as the world leader in advanced carbon-free technologies. We hope to continue our excellent nuclear tradition by hosting the ANS Student Conference in 2021. 
\clearpage

\subsubsection{Accessibility and Accomodation}
 A large number of hotels are located around downtown Champaign and the Eastern side of campus, making transportation easy. Champaign-Urbana Mass Transit (CU-MTD) is a reliable public transportation service that sees millions of riders every year. CU-MTD charges an affordable rate of \$1 per ride. All CU-MTD busses are wheelchair accessible. Rental bikes and rideshare services are also plentiful. There is a small airport, Willard Airport, just 20 minutes from campus that has regular flights to and from Chicago O’Hare and Dallas Fort Worth airports. Finally, Peoria Charter is a popular bus service with several daily trips between the UIUC campus and the Chicagoland area.
